\section*{International journals}
    \subsection*{Published}
    \begin{itemize}
        \item Merbecks T., Leal A.M.M, Bombarda P., Silva P., Alfani D., Saar M. O. "GeoProp: A thermophysical property modelling framework for single and two-phase geothermal geofluids". \textit{Geothermics} 
    \end{itemize}

% doi: 10.1016/j.geothermics.2024.103146

\section*{International conference proceedings}
    \begin{itemize}
        \item Merbecks T., Bombarda P., Saar M. O., Silva P., Alfani D. "Investigating the design of ORC heat introduction for single- and two-phase geofluid brines with and without non-condensable gases". \textit{Proceedings of the European Geothermal Congress 2022}
        \item Merbecks T., Pietra C., Bombarda P., Saar M. O., Silva P., Alfani D. "Investigating the application range of ORC power plants for the exploitation of two-phase geothermal resources". \textit{Proceedings of the ORC 2023} doi: 10.12795/9788447227457\_104
        
        \item Merbecks T., Bombarda P., Silva P., Alfani D. "On the thermodynamic and economic performance of binary power plant configurations for the exploitation of two-phase geothermal resources". \textit{Proceedings of the Stanford Geothermal Workshop 2024}
    \end{itemize}

\section*{Conference presentations \& posters}
    \begin{itemize}
        \item Merbecks T., Bombarda P., Saar M. O., Silva P., Alfani D. "Design and Operation of a Binary ORC Plant for the Exploitation of Different Geothermal Sources, Including Two-Phase Sources". \textit{EGPD 2022} - Poster
        \item Merbecks T., Bombarda P., Saar M. O., Silva P., Alfani D. "A novel thermophysical property model for single and two-phase geothermal brines and non-condensable gas". \textit{EGPD 2023} - Poster \& Presentation
        \item Merbecks T., Pietra C., Bombarda P., Saar M. O., Silva P., Alfani D. "Investigating the thermodynamic application envelope of different geothermal power plant technologies and configurations". \textit{EGPD 2023} - Poster
        \item Merbecks T., Galieti L., Bombarda P., Saar M. O., Silva P., Alfani D. de Servi C., Colonna P. "On novel binary power plant configurations for the exploitation of two-phase geothermal resources". \textit{EGW 2023} - Poster \& Presentation
    \end{itemize}


\section*{Easygo Workshops}
    \begin{itemize}
        \item 1\textsuperscript{st} Training Week. Delft, Netherlands. 2021
        \item 2\textsuperscript{nd} Training Week. Aachen, Germany. 2022
        \item 3\textsuperscript{rd} Training Week. Volterra, Italy. 2023
        \item Final Training Week. Zurich, Switzerland. 2024
    \end{itemize}

\section*{Easygo deliverables}
    \begin{itemize}
        \item Merbecks T., Bombarda P., Saar M. O., Silva P., Alfani D. "D1.7: Thermodynamic model of fluid mixtures including \ce{CO2}".
        \item EASYGO-ITN, Kottsova, A., Luo, W., Naranjo, D., Eltayieb, M., Galieti, L. Söding, H., Rangel Jurado, N., Türkdoğan, S., Ouf, J., Santoso, R., Balza Morales, A.E., Gómez Diaz, E., Merbecks, T. "D4.2: Geothermal energy - an introduction to the topic and key issues". \url{https://easygo-itn.github.io/Deliverable_4_2/}
        \item Merbecks T., Bombarda P., Saar M. O., Silva P., Alfani D. "D1.14: Report on optimised operating conditions and maintenance strategy for geothermal plants operating with two-phase fluids at real scale".
    \end{itemize}